
\title{Average}
\author{Rajesh Kumar}
\date{}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Definition}
  \begin{itemize}
    \item \textbf{Average:} A measure of central tendency that represents the typical value of a set of numbers.
  \end{itemize}
\end{frame}

\begin{frame}{Introduction}
  \begin{itemize}
    \item The average is commonly used to represent the central value of a set of data points.
    \item It provides a single value that summarizes the data and is often used for comparison and analysis.
  \end{itemize}
\end{frame}

\begin{frame}{Where it is Used in Real Life}
  \begin{itemize}
    \item \textbf{Grades:} Average scores in academic assessments.
    \item \textbf{Finance:} Average returns on investments.
    \item \textbf{Sports:} Average performance statistics for athletes.
  \end{itemize}
\end{frame}

\begin{frame}{Worked Out Problems}
  \textbf{Problem 1:} The scores of a student in five subjects are $85, 90, 88, 92,$ and $87.$ Calculate the average score.

  \textbf{Solution:}
  \begin{enumerate}
    \item \textbf{Given:} Scores $= 85, 90, 88, 92, 87$.
    \item \textbf{Formula:} The average is calculated as $\frac{\text{Sum of Scores}}{\text{Number of Scores}}$.
    \item \textbf{Calculate:} Average $= \frac{85 + 90 + 88 + 92 + 87}{5}$.
  \end{enumerate}
\end{frame}

\begin{frame}{Reasoning for Average Solution}
  \begin{itemize}
    \item The average is found by summing up all the scores and dividing by the number of scores.
    \item For the given problem, the average score is $\frac{85 + 90 + 88 + 92 + 87}{5}$.
    \item This provides a single value that represents the typical score of the student.
  \end{itemize}
\end{frame}

\begin{frame}{Exercise for Students}
  \begin{enumerate}
    \item Find the average of $12, 15, 18, 20,$ and $25$.
    \item A car travels at speeds of $50, 60, 55, 65,$ and $70$ mph. Calculate the average speed.
    \item Discuss a real-life scenario where understanding averages is important.
  \end{enumerate}
\end{frame}

