\title{Linear Equations}
\author{Rajesh Kumar}
\date{}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Definition}
  \begin{itemize}
    \item \textbf{Linear Equation:} An equation that represents a straight line when graphed on a coordinate plane.
  \end{itemize}
\end{frame}

\begin{frame}{Introduction}
  \begin{itemize}
    \item Linear equations are fundamental in algebra and represent relationships between variables that result in a straight-line graph.
    \item They are used to model various real-world situations and are crucial in problem-solving.
  \end{itemize}
\end{frame}

\begin{frame}{Where it is Used in Real Life}
  \begin{itemize}
    \item \textbf{Finance:} Budgeting and financial planning often involve linear relationships.
    \item \textbf{Physics:} Formulas describing motion or energy can be represented by linear equations.
    \item \textbf{Engineering:} Many engineering problems are modeled using linear equations.
  \end{itemize}
\end{frame}

\begin{frame}{Worked Out Problems}
  \textbf{Problem 1:} Solve the equation $2x + 3 = 7$.

  \textbf{Solution:}
  \begin{enumerate}
    \item \textbf{Equation:} $2x + 3 = 7$.
    \item \textbf{Isolate Variable:} Subtract $3$ from both sides to get $2x = 4$.
    \item \textbf{Solve for $x$:} Divide both sides by $2$ to find $x = 2$.
  \end{enumerate}
\end{frame}

\begin{frame}{Reasoning for Linear Equation Solution}
  \begin{itemize}
    \item To solve a linear equation, perform operations to isolate the variable on one side of the equation.
    \item For the given problem, start by subtracting $3$ from both sides, resulting in $2x = 4$.
    \item Then, divide both sides by $2$ to find $x = 2$.
  \end{itemize}
\end{frame}

\begin{frame}{Exercise for Students}
  \begin{enumerate}
    \item Solve the equation $3y - 5 = 10$.
    \item Write a linear equation to represent the statement: "Twice a number increased by $7$ is equal to $15$."
    \item Discuss a real-life scenario where understanding linear equations is important.
  \end{enumerate}
\end{frame}

