\title{Profit and Loss}
\author{Rajesh Kumar}
\date{}

\begin{frame}{Definition}
  \begin{itemize}
    \item \textbf{Profit:} The financial gain made in a transaction.
    \item \textbf{Loss:} The financial deficit incurred in a transaction.
  \end{itemize}
\end{frame}

\begin{frame}{Introduction}
  \begin{itemize}
    \item Profit and loss are essential concepts in business and everyday transactions.
    \item Understanding these concepts helps in making informed financial decisions.
  \end{itemize}
\end{frame}

\begin{frame}{Where it is Used in Real Life}
  \begin{itemize}
    \item \textbf{Profit:} Business transactions, investments, selling goods.
    \item \textbf{Loss:} Business losses, investments with negative returns, selling goods at a loss.
  \end{itemize}
\end{frame}

\begin{frame}{Worked Out Problems}
  \textbf{Problem 1:} A person buys a product for $\$50$ and sells it for $\$80$. Calculate the profit.

  \textbf{Solution:}
  \begin{enumerate}
    \item \textbf{Given:} Cost Price (CP) = $50$, Selling Price (SP) = $80$.
    \item \textbf{Formula:} Profit ($P$) is calculated as $P = SP - CP$.
    \item \textbf{Substitute:} $P = 80 - 50$.
    \item \textbf{Calculate:} $P = 30$.
  \end{enumerate}
\end{frame}

\begin{frame}{Exercise for Students}
  \begin{enumerate}
    \item Calculate the profit if an item is bought for $\$120$ and sold for $\$150$.
    \item Determine the loss if an article is purchased for $\$90$ and sold for $\$80$.
    \item Discuss a real-life scenario where understanding profit and loss is important.
  \end{enumerate}
\end{frame}

