\title{Partnership}
\author{Rajesh Kumar}
\date{}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Definition}
  \begin{itemize}
    \item \textbf{Partnership:} A business structure where two or more individuals manage and operate a business in accordance with the terms and objectives set out in a Partnership Deed.
  \end{itemize}
\end{frame}

\begin{frame}{Introduction}
  \begin{itemize}
    \item Partnership is a form of business organization that allows multiple individuals to share responsibilities and profits.
    \item Partnerships are governed by a legal agreement known as the Partnership Deed.
  \end{itemize}
\end{frame}

\begin{frame}{Where it is Used in Real Life}
  \begin{itemize}
    \item \textbf{Small Businesses:} Many small businesses, such as law firms, medical practices, and consulting firms, operate as partnerships.
    \item \textbf{Professional Services:} Partnerships are common in professional services where expertise and collaboration are essential.
  \end{itemize}
\end{frame}

\begin{frame}{Worked Out Problems}
  \textbf{Problem 1:} In a partnership, John invests $\$5000$ and Peter invests $\$7000$. If the total profit at the end of the year is $\$6000$, how much does each partner receive?

  \textbf{Solution:}
  \begin{enumerate}
    \item \textbf{Given:} John's investment = $\$5000$, Peter's investment = $\$7000$, Total profit = $\$6000$.
    \item \textbf{Formula:} Share of each partner is calculated as their investment divided by the total investment, multiplied by the total profit.
    \item \textbf{John's Share:} $\frac{5000}{5000 + 7000} \times 6000$.
    \item \textbf{Peter's Share:} $\frac{7000}{5000 + 7000} \times 6000$.
  \end{enumerate}
\end{frame}

\begin{frame}{Reasoning for Partnership Solution}
  \begin{itemize}
    \item In a partnership, the distribution of profits is based on the proportion of each partner's investment.
    \item John's share is calculated as $\frac{5000}{5000 + 7000} \times 6000$, and Peter's share is calculated as $\frac{7000}{5000 + 7000} \times 6000$.
    \item The total profit is distributed among the partners according to their investments.
  \end{itemize}
\end{frame}

\begin{frame}{Exercise for Students}
  \begin{enumerate}
    \item If two partners, A and B, invest $\$8000$ and $\$12000$ respectively in a business, and the annual profit is $\$5000$, calculate the share of each partner.
    \item Discuss a real-life scenario where forming a partnership would be beneficial for a business.
  \end{enumerate}
\end{frame}

