
\title{Percentage}
\author{Rajesh Kumar}
\date{}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Definition}
  \begin{itemize}
    \item \textbf{Percentage:} A proportion or ratio expressed as a fraction of 100.
  \end{itemize}
\end{frame}

\begin{frame}{Introduction}
  \begin{itemize}
    \item Percentage is a common way to express a part of a whole in terms of 100.
    \item It is used in various real-life situations for comparisons and calculations.
  \end{itemize}
\end{frame}

\begin{frame}{Where it is Used in Real Life}
  \begin{itemize}
    \item \textbf{Discounts:} Percentage off on retail prices.
    \item \textbf{Interest Rates:} Mortgage rates, credit card interest rates.
    \item \textbf{Grades:} Academic scores are often presented as percentages.
  \end{itemize}
\end{frame}

\begin{frame}{Worked Out Problems}
  \textbf{Problem 1:} If a shirt originally costs $\$40$ and is discounted by $20\%$, find the discounted price.

  \textbf{Solution:}
  \begin{enumerate}
    \item \textbf{Given:} Original Price = $\$40$, Discount Rate = $20\%$.
    \item \textbf{Formula:} Discounted Price ($DP$) is calculated as $DP = \text{Original Price} - (\text{Original Price} \times \text{Discount Rate})$.
    \item \textbf{Substitute:} $DP = 40 - (40 \times 0.2)$.
    \item \textbf{Calculate:} $DP = 40 - 8 = 32$.
  \end{enumerate}
\end{frame}

\begin{frame}{Exercise for Students}
  \begin{enumerate}
    \item Calculate $15\%$ of $\$120$.
    \item A student scored $85\%$ on a test. If the total marks were $200$, how many marks did the student score?
    \item Discuss a real-life scenario where understanding percentages is important.
  \end{enumerate}
\end{frame}

