\title{Surface Area}
\author{Rajesh Kumar}
\date{}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Definition}
  \begin{itemize}
    \item \textbf{Surface Area:} The total area of the surface of a three-dimensional object.
  \end{itemize}
\end{frame}

\begin{frame}{Introduction}
  \begin{itemize}
    \item Surface area is a crucial measure in geometry and is used to quantify the extent of the outer layer of three-dimensional shapes.
    \item Understanding surface area is essential for various applications, such as construction, packaging, and manufacturing.
  \end{itemize}
\end{frame}

\begin{frame}{Where it is Used in Real Life}
  \begin{itemize}
    \item \textbf{Packaging:} Determining the amount of material needed for packaging.
    \item \textbf{Construction:} Calculating the amount of paint or other materials required to cover surfaces.
    \item \textbf{Manufacturing:} Designing products with optimized surface area for efficiency.
  \end{itemize}
\end{frame}

\begin{frame}{Worked Out Problems}
  \textbf{Problem 1:} Find the surface area of a rectangular prism with dimensions $length = 4$, $width = 3$, and $height = 5$.

  \textbf{Solution:}
  \begin{enumerate}
    \item \textbf{Formula:} The surface area of a rectangular prism is given by $2lw + 2lh + 2wh$.
    \item \textbf{Substitute:} Surface area $= 2(4 \times 3) + 2(4 \times 5) + 2(3 \times 5)$.
    \item \textbf{Calculate:} Surface area $= 24 + 40 + 30 = 94$.
  \end{enumerate}
\end{frame}

\begin{frame}{Reasoning for Surface Area Solution}
  \begin{itemize}
    \item The formula for the surface area of a rectangular prism is $2lw + 2lh + 2wh$.
    \item Substitute the given dimensions into the formula and calculate each term separately.
    \item Summing up the individual areas gives the total surface area of the rectangular prism.
  \end{itemize}
\end{frame}

\begin{frame}{Exercise for Students}
  \begin{enumerate}
    \item Find the surface area of a cube with a side length of $6$ units.
    \item Calculate the surface area of a cylinder with a radius of $4$ units and a height of $8$ units.
    \item Discuss a real-life scenario where understanding surface area is crucial.
  \end{enumerate}
\end{frame}

