\documentclass[a4paper, 12pt]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{amssymb, amsmath, graphicx, tabularx, booktabs, subfiles, amsthm,enumitem,xcolor,appendix}
 

\newcommand{\ans}[1]{\textcolor{red}{#1}}

\newcommand{\boxx}[1]{%
    \begin{tcolorbox}[colback=gray!10, colframe=gray!50, title=Where it is getting wrong?]
        #1
    \end{tcolorbox}%
}


\title{}
\author{}

\begin{document}
\maketitle
%------------Body-Starts--------------------


\section*{Files, Registers, and Application Formats for HoD Physics}

\subsection*{Faculty Files:}
\begin{enumerate}
  \item Personal and contact information for each faculty member.
  \item Academic credentials, certifications, and professional achievements.
  \item Teaching and research portfolios.
  \item Records of professional development activities.
\end{enumerate}

\subsection*{Staff Records:}
\begin{enumerate}
  \item Information about administrative and support staff within the department.
  \item Job descriptions, roles, and responsibilities.
  \item Attendance and leave records.
\end{enumerate}

\subsection*{Course Files:}
\begin{enumerate}
  \item Curriculum and syllabi for each course offered by the department.
  \item Lecture schedules, course outlines, and teaching materials.
  \item Assessment and examination records.
\end{enumerate}

\subsection*{Research and Publications:}
\begin{enumerate}
  \item Records of faculty research projects.
  \item Publications, conference presentations, and research outputs.
  \item Grant applications and funding information.
\end{enumerate}

\subsection*{Meeting Records:}
\begin{enumerate}
  \item Minutes of departmental meetings.
  \item Agendas for upcoming meetings.
  \item Action items and follow-up tasks.
\end{enumerate}

\subsection*{Financial Records:}
\begin{enumerate}
  \item Budgets and financial reports.
  \item Expenditure records.
  \item Funding sources and grants.
\end{enumerate}

\subsection*{Student Records:}
\begin{enumerate}
  \item Academic performance records.
  \item Attendance records.
  \item Graduation and placement data.
\end{enumerate}

\subsection*{Equipment and Facilities:}
\begin{enumerate}
  \item Inventory of laboratory equipment.
  \item Maintenance records for facilities.
  \item Requests for new equipment or facility upgrades.
\end{enumerate}

\subsection*{Collaboration and Outreach:}
\begin{enumerate}
  \item Records of collaborations with other departments or institutions.
  \item Outreach programs, community engagement, and public relations activities.
\end{enumerate}

\subsection*{Accreditation and Compliance:}
\begin{enumerate}
  \item Documentation related to accreditation processes.
  \item Compliance with academic standards and regulations.
\end{enumerate}

\subsection*{Correspondence and Communications:}
\begin{enumerate}
  \item Internal and external communications related to the department.
  \item Correspondence with faculty, staff, students, and external entities.
\end{enumerate}









%------------Body-Ends--------------------
%\bibliography{ref.bib}
%\bibliographystyle{IEEEtran}
\end{document}
