
\title{Introduction to Computer Systems}
\author{Rajesh Kumar}
\date{}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Overview}
  \begin{itemize}
    \item Computers are fundamental to modern life, playing a crucial role in various fields.
    \item Introduction to the basic concepts and components of a computer system.
  \end{itemize}
\end{frame}

\begin{frame}{Definition}
  \begin{itemize}
    \item A computer system is an integrated set of hardware and software components that work together to process data and perform tasks.
    \item Computers range from personal devices to large-scale servers and supercomputers.
  \end{itemize}
\end{frame}

\begin{frame}{Components of a Computer System}
  \begin{enumerate}
    \item \textbf{Central Processing Unit (CPU):} The brain of the computer, responsible for executing instructions.
    \item \textbf{Memory:} Storage for data and instructions needed by the CPU.
    \item \textbf{Storage:} Devices for long-term data storage (e.g., hard drives, SSDs).
    \item \textbf{Input Devices:} Tools for entering data into the computer (e.g., keyboard, mouse).
    \item \textbf{Output Devices:} Tools for receiving information from the computer (e.g., monitor, printer).
  \end{enumerate}
\end{frame}

\begin{frame}{Software}
  \begin{itemize}
    \item \textbf{Operating System:} Manages hardware resources and provides a user interface.
    \item \textbf{Applications:} Software programs designed for specific tasks (e.g., word processors, web browsers).
  \end{itemize}
\end{frame}

\begin{frame}{Types of Computers}
  \begin{enumerate}
    \item \textbf{Personal Computers (PCs):} Designed for individual use (e.g., desktops, laptops).
    \item \textbf{Servers:} Provide services or resources to other computers in a network.
    \item \textbf{Mainframes:} Powerful computers used for large-scale data processing.
    \item \textbf{Supercomputers:} Extremely high-performance computers for complex calculations (e.g., scientific simulations).
  \end{enumerate}
\end{frame}

\begin{frame}{How Computers Work}
  \begin{itemize}
    \item Computers follow the basic input-process-output model.
    \item Instructions are executed by the CPU, with data flowing between memory, storage, and input/output devices.
  \end{itemize}
\end{frame}

\begin{frame}{Conclusion}
  \begin{itemize}
    \item Understanding the components and functions of a computer system is foundational for anyone interacting with technology.
    \item Further exploration into computer architecture and advanced concepts can deepen this understanding.
  \end{itemize}
\end{frame}
