\title{Components of a Computer}
\author{Rajesh Kumar}
\date{}


\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Overview}
  \begin{itemize}
    \item A computer is a complex system made up of several interconnected components.
    \item Introduction to the key components that constitute a computer system.
  \end{itemize}
\end{frame}

\begin{frame}{Central Processing Unit (CPU)}
  \begin{itemize}
    \item \textbf{Function:} The brain of the computer, responsible for executing instructions.
    \item \textbf{Components:} Control Unit, Arithmetic Logic Unit (ALU), Registers.
    \item \textbf{Characteristics:} Processing speed is a critical factor.
  \end{itemize}
\end{frame}

\begin{frame}{Memory}
  \begin{itemize}
    \item \textbf{RAM (Random Access Memory):} Temporary storage for actively running programs and data.
    \item \textbf{ROM (Read-Only Memory):} Non-volatile memory containing essential system instructions.
    \item \textbf{Cache Memory:} Faster, smaller memory for frequently accessed data.
  \end{itemize}
\end{frame}

\begin{frame}{Storage Devices}
  \begin{itemize}
    \item \textbf{Hard Disk Drives (HDDs):} Magnetic storage for long-term data.
    \item \textbf{Solid State Drives (SSDs):} Flash memory-based storage for faster access.
    \item \textbf{Optical Drives:} Read and write data on optical discs (CDs, DVDs, Blu-rays).
  \end{itemize}
\end{frame}

\begin{frame}{Input Devices}
  \begin{itemize}
    \item \textbf{Keyboard:} Entering text and commands.
    \item \textbf{Mouse:} Pointing and clicking for navigation.
    \item \textbf{Scanner:} Converting physical documents into digital format.
    \item \textbf{Webcam:} Capturing video input.
  \end{itemize}
\end{frame}

\begin{frame}{Output Devices}
  \begin{itemize}
    \item \textbf{Monitor:} Displaying visual output.
    \item \textbf{Printer:} Producing hard copy output.
    \item \textbf{Speakers:} Outputting audio.
  \end{itemize}
\end{frame}

\begin{frame}{Motherboard}
  \begin{itemize}
    \item \textbf{Function:} Main circuit board connecting all components.
    \item \textbf{Components:} CPU socket, Memory slots, Expansion slots, Input/Output ports.
  \end{itemize}
\end{frame}

\begin{frame}{Power Supply}
  \begin{itemize}
    \item \textbf{Function:} Converts electrical power from an outlet into usable power for the computer.
    \item \textbf{Components:} Transformer, Capacitors, Voltage Regulator.
  \end{itemize}
\end{frame}

\begin{frame}{Conclusion}
  \begin{itemize}
    \item Each component plays a crucial role in the overall functionality of a computer system.
    \item Understanding the interaction between these components is essential for effective troubleshooting and system optimization.
  \end{itemize}
\end{frame}
