\title{Generations of Computers}
\author{Rajesh Kumar}
\date{}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Overview}
  \begin{itemize}
    \item The evolution of computers is categorized into generations, each marked by significant technological advancements.
    \item Introduction to the four generations of computers.
  \end{itemize}
\end{frame}

\begin{frame}{First Generation (1940s-1950s)}
  \begin{itemize}
    \item \textbf{Vacuum Tubes:} Main electronic component.
    \item \textbf{Size:} Large and cumbersome.
    \item \textbf{Examples:} ENIAC, UNIVAC.
    \item \textbf{Characteristics:} Batch processing, limited programming languages.
  \end{itemize}
\end{frame}

\begin{frame}{Second Generation (1950s-1960s)}
  \begin{itemize}
    \item \textbf{Transistors:} Replaced vacuum tubes, smaller and more reliable.
    \item \textbf{Size:} Smaller and more efficient.
    \item \textbf{Examples:} IBM 1401, CDC 1604.
    \item \textbf{Characteristics:} Introduction of high-level programming languages (Fortran, COBOL), faster processing.
  \end{itemize}
\end{frame}

\begin{frame}{Third Generation (1960s-1970s)}
  \begin{itemize}
    \item \textbf{Integrated Circuits (ICs):} Multiple transistors on a single chip.
    \item \textbf{Size:} Significant reduction in size.
    \item \textbf{Examples:} IBM System/360, DEC PDP-11.
    \item \textbf{Characteristics:} More powerful, support for time-sharing, development of operating systems.
  \end{itemize}
\end{frame}

\begin{frame}{Fourth Generation (1970s-Present)}
  \begin{itemize}
    \item \textbf{Microprocessors:} Integration of entire CPU on a single chip.
    \item \textbf{Size:} Very small and portable.
    \item \textbf{Examples:} Personal computers, laptops, smartphones.
    \item \textbf{Characteristics:} Vastly improved speed and efficiency, graphical user interfaces, widespread use of personal computers.
  \end{itemize}
\end{frame}

\begin{frame}{Fifth Generation (Emerging)}
  \begin{itemize}
    \item \textbf{Artificial Intelligence:} Focus on AI and machine learning.
    \item \textbf{Examples:} Advanced robotics, natural language processing, neural networks.
    \item \textbf{Characteristics:} Emphasis on parallel processing, AI applications, advanced human-computer interactions.
  \end{itemize}
\end{frame}

\begin{frame}{Conclusion}
  \begin{itemize}
    \item The evolution of computers reflects a continual quest for smaller, faster, and more powerful technology.
    \item Ongoing advancements in technology suggest a future beyond the traditional generational classification.
  \end{itemize}
\end{frame}
