\title{Types of Computers}
\author{Rajesh Kumar}
\date{}


\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Overview}
  \begin{itemize}
    \item Computers come in various forms, each designed for specific purposes and applications.
    \item Introduction to the common types of computers based on size, functionality, and usage.
  \end{itemize}
\end{frame}

\begin{frame}{Personal Computers (PCs)}
  \begin{itemize}
    \item \textbf{Description:} Designed for individual use.
    \item \textbf{Examples:} Desktops, laptops, workstations.
    \item \textbf{Characteristics:} Versatile, used for general computing tasks, personal productivity, and entertainment.
  \end{itemize}
\end{frame}

\begin{frame}{Servers}
  \begin{itemize}
    \item \textbf{Description:} Provide services or resources to other computers in a network.
    \item \textbf{Examples:} Web servers, file servers, database servers.
    \item \textbf{Characteristics:} Powerful, designed for reliability and high-performance, handle multiple requests from clients.
  \end{itemize}
\end{frame}

\begin{frame}{Mainframes}
  \begin{itemize}
    \item \textbf{Description:} Large and powerful computers for heavy-duty data processing.
    \item \textbf{Examples:} IBM System z series.
    \item \textbf{Characteristics:} High processing power, used for critical applications like financial transactions, airline reservations.
  \end{itemize}
\end{frame}

\begin{frame}{Supercomputers}
  \begin{itemize}
    \item \textbf{Description:} Extremely high-performance computers for complex calculations.
    \item \textbf{Examples:} IBM Summit, Cray XT5.
    \item \textbf{Characteristics:} Top-tier processing power, used for scientific simulations, weather modeling, and advanced research.
  \end{itemize}
\end{frame}

\begin{frame}{Embedded Computers}
  \begin{itemize}
    \item \textbf{Description:} Integrated into other devices or systems.
    \item \textbf{Examples:} Smartphones, smart appliances, automotive control systems.
    \item \textbf{Characteristics:} Specialized, dedicated to specific functions, often part of a larger system.
  \end{itemize}
\end{frame}

\begin{frame}{Wearable Computers}
  \begin{itemize}
    \item \textbf{Description:} Worn on the body, providing continuous access to information.
    \item \textbf{Examples:} Smartwatches, fitness trackers, augmented reality glasses.
    \item \textbf{Characteristics:} Portable, designed for convenience, often include sensors for health monitoring.
  \end{itemize}
\end{frame}

\begin{frame}{Conclusion}
  \begin{itemize}
    \item The diversity of computer types reflects the broad range of applications and user needs.
    \item Ongoing technological advancements continue to expand the capabilities of each type of computer.
  \end{itemize}
\end{frame}
