
\title{Introduction}
\author{Rajesh Kumar}
\date{}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Definition}
  \begin{itemize}
    \item \textbf{Probability:} A measure of the likelihood that a specific event will occur, expressed as a number between 0 and 1.
  \end{itemize}
\end{frame}

\begin{frame}{Introduction}
  \begin{itemize}
    \item Probability is a fundamental concept in mathematics that deals with uncertainty and randomness.
    \item It is widely used in various fields, including statistics, finance, and science.
  \end{itemize}
\end{frame}

\begin{frame}{Where it is Used in Real Life}
  \begin{itemize}
    \item \textbf{Gaming:} Probability is crucial in games of chance, such as dice games or card games.
    \item \textbf{Weather Forecasting:} Probability is used to predict the likelihood of weather events.
    \item \textbf{Medical Diagnostics:} Probability is employed in assessing the likelihood of certain medical conditions.
  \end{itemize}
\end{frame}

\begin{frame}{Worked Out Problems}
  \textbf{Problem 1:} If you roll a fair six-sided die, what is the probability of rolling a 4?

  \textbf{Solution:}
  \begin{enumerate}
    \item \textbf{Possible Outcomes:} There are 6 possible outcomes (numbers 1 through 6).
    \item \textbf{Favorable Outcomes:} Rolling a 4 is one favorable outcome.
    \item \textbf{Probability:} The probability is calculated as $\frac{\text{Favorable Outcomes}}{\text{Possible Outcomes}}$.
    \item \textbf{Calculate:} Probability $= \frac{1}{6}$.
  \end{enumerate}
\end{frame}

\begin{frame}{Reasoning for Probability Solution}
  \begin{itemize}
    \item Probability is the ratio of favorable outcomes to possible outcomes.
    \item For the given problem, rolling a 4 is one favorable outcome out of 6 possible outcomes.
    \item The probability of rolling a 4 is $\frac{1}{6}$.
  \end{itemize}
\end{frame}

\begin{frame}{Exercise for Students}
  \begin{enumerate}
    \item If you flip a fair coin, what is the probability of getting heads?
    \item A standard deck of cards has 52 cards. What is the probability of drawing a spade?
    \item Discuss a real-life scenario where understanding probability is important.
  \end{enumerate}
\end{frame}
